Modelling writing hesitations in text writing as finite mixture process

### 2023-02-07 report/results.Rmd
Upload mixture model tutorial

```{r include = F}
library(tidyverse)
library(kableExtra)
library(janitor)
library(brms)
library(polspline)
library(patchwork)
library(rmdformats)
library(gridExtra)
library(grid)
library(gtable)
library(gridExtra)
library(scales)
library(caret)
library(InformationValue)

@@

theme_set(theme_bw(base_size = 14) +
            theme(strip.background = element_blank(),
                  legend.position = "top",
                  legend.justification = "right",
                  panel.grid = element_blank(),
                  panel.background = element_rect(fill = "transparent"), # bg of the panel
                  plot.background = element_rect(fill = "transparent", color = NA)))

@@

@@

## Data processing

@@

# PlanTra

@@

## Data processing

@@

```{r predictionsplantra, fig.cap="PlanTra data. Comparison of 100 simulated (predicted) sets of data to observed data illustated by model. For illustration the x-axis was truncated at 2,000 msecs."}

@@

kable(table, caption = "PlanTra data. Model comparisons. The top row shows the models with the highest predictive performance. Standard error is shown in parentheses.",
        align =c("l", rep("r", 8))) %>%
  kable_styling(position = "center", 
                full_width = T, 
                font_size = 11) %>%
  footnote("$\\widehat{elpd}$ = predictive performance indicated as expected log pointwise predictive density; $\\Delta\\widehat{elpd}$ = difference in predictive performance relative to the model with the highest predictive performance in the top row.") %>%
  add_header_above(c(" " = 1, 
                     "All transitions" = 2,
                     "Before sentence" = 2, 
                     "Before word" = 2,
                     "Within word" = 2)) %>%
  column_spec(1, width = "8em")

@@

```{r plantrapost, fig.cap="PlanTra. Posterior parameter distribution"}
file <- list.files(path = "../stanout/plantra", pattern = "mog.csv$",full.names = T)
ps <- read_csv(file) %>% 
  mutate(across(task, factor, levels = c("pre-test", "post-test"), ordered = T)) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(delta, ~.+beta),
         across(c(delta, beta), exp),
         across(delta, ~.-beta),
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(beta:prob) %>% 
  group_by(task, location, name) %>% 
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"))

beta <- filter(ps, name == "beta") %>% 
  mutate(name = beta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = c(21, 23)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "Posterior estimate with 95% PIs",
       x = "",
       colour = "Task",
       shape = "Task")

delta <- filter(ps, name == "delta") %>% 
  mutate(name = delta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = c(21, 23)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "",
       x = "Transition location",
       colour = "Task",
       shape = "Task") +
  theme(axis.title.y = element_blank())

theta <- filter(ps, name == "prob") %>% 
  mutate(name = theta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = c(21, 23)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = dezero_plot, limits = c(0, 1)) +
  labs(y = "",
       x = "",
       colour = "Task",
       shape = "Task") +
  theme(axis.title.y = element_blank())

@@

## Data processing

@@

```{r}
files <- str_c("../stanout/", c("lift", "spl2", "plantra"), "/mog.csv")
ps <- purrr::map_dfr(files, ~read_csv(.x) %>% 
  mutate(data = .x)) %>% 
  mutate(across(data, str_remove_all, "\\.|\\/|stanout|\\mog.csv"),
         across(data, recode_factor, 
                "spl2" = "SPL2", 
                "plantra" = "PlanTra",
                "lift" = "LIFT", 
                .ordered = TRUE)) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(delta, ~.+beta),
         across(c(delta, beta), exp),
         across(delta, ~.-beta),
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(beta:prob) %>% 
  group_by(data, location, name) %>% 
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper),
                   .names = "{.fn}")) %>% 
  ungroup()
```

```{r crossstudypost, fig.cap="Across studies. Posterior parameter distribution"}
posd <- position_dodge(.65)
dotsize <- 2.5
grouplabel <- "Data set"
beta <- filter(ps, name == "beta") %>% 
  mutate(name = beta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = data,
             shape = data)) +
  geom_point(size = dotsize, position = posd) +
  geom_errorbar(width = 0, position = posd) +
  facet_grid(~name) +
  scale_shape_manual(values = c(1, 4, 7)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "Posterior estimate with 95% PIs",
       x = "",
       colour = grouplabel,
       shape = grouplabel)

delta <- filter(ps, name == "delta") %>% 
  mutate(name = delta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = data,
             shape = data)) +
  geom_point(size = dotsize, position = posd) +
  geom_errorbar(width = 0, position = posd) +
  facet_grid(~name) +
  scale_shape_manual(values = c(1, 4, 7)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "",
       x = "Transition location",
       colour = grouplabel,
       shape = grouplabel) +
  theme(axis.title.y = element_blank())

theta <- filter(ps, name == "prob") %>% 
  mutate(name = theta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = data,
             shape = data)) +
  geom_point(size = dotsize, position = posd) +
  geom_errorbar(width = 0, position = posd) +
  facet_grid(~name) +
  scale_shape_manual(values = c(1, 4, 7)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = dezero_plot, limits = c(0, 1)) +
  labs(y = "",
       x = "",
       colour = grouplabel,
       shape = grouplabel) +
  theme(axis.title.y = element_blank())

@@

```{r eval = F}
# use posterior to calculate interactions, cell means and dataset differences
files <- str_c("../stanout/", c("lift", "spl2", "plantra"), "/mog.csv")

@@

ps <- bind_rows(plantra, spl2, lift) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(data, 
                str_remove_all, 
                "\\.|\\/|stanout|\\mog.csv"),
         theta = logit_scaled(prob)) %>% 
  select(-prob) %>%
  pivot_longer(beta:theta) %>%
  pivot_wider(names_from = c(data, location), 
              values_from = value, 
              names_sep = "_") %>% 
  unnest(contains("_"))

# Get main effects, interactions, nested effects
ps_effects <- ps %>%
  rowwise() %>%
  mutate(# Main effects
         DS_1 = mean(c_across(starts_with("lift_"))) - 
                mean(c_across(starts_with("spl2_"))),
         DS_2 = mean(c_across(starts_with("lift_"))) - 
                mean(c_across(starts_with("plantra_"))),
         DS_3 = mean(c_across(starts_with("spl2_"))) - 
                mean(c_across(starts_with("plantra_"))),
         TL_1 =  mean(c_across(contains(" sentence"))) - 
                mean(c_across(contains("_before word"))),
         TL_2 =  mean(c_across(contains("_before"))) - 
                mean(c_across(contains("_within word"))),
         # Two-way interactions
         `DS_1:TL_1` = (`lift_before sentence` - `lift_before word`) -
                       (`spl2_before sentence` - `spl2_before word`),

@@

@@

```{r cellmeans, results = 'asis'}
tmp <- read_csv("tables/cellmeans_transdur.csv") %>% 
  mutate(across(Contrasts, str_replace, "lift", "LIFT"),
         across(Contrasts, str_replace, "spl2", "SPL2"),
         across(Contrasts, str_replace, "plantra", "PlanTra"))

>>>>

```{r include = F}
library(tidyverse)
library(kableExtra)
library(janitor)
library(brms)
library(polspline)
library(patchwork)
library(rmdformats)
library(gridExtra)
library(grid)
library(gtable)
library(gridExtra)
library(scales)
#library(caret)
#library(InformationValue)

@@

theme_set(theme_bw(base_size = 12) +
            theme(strip.background = element_blank(),
                  legend.position = "top",
                  legend.justification = "right",
                  panel.grid = element_blank(),
                  panel.background = element_rect(fill = "transparent"), # bg of the panel
                  plot.background = element_rect(fill = "transparent", color = NA)))

@@

# Data processing

TODO: Add a description with general data filtering and a table with how many data were removed from the analysis by study.

# C2L1

The C2L1 data set comprises data Norwegian 6th graders--*N*=133, mean age 11 years 10 months--published in @ronneberg2022process. The children composed argumentative essays in Norwegian, a language with a relatively shallow orthography.

```{r eval = F}
d <- read_csv("../data/c2l1.csv") %>%
  filter(!is.na(iki), 
         iki > 50, 
         iki < 30000) %>%
  mutate(ppt = as.numeric(factor(subno)),
         condition = factor(str_c(location, sep = "_")),
         cond_num = as.integer(condition)) %>% 
  select(ppt, iki, condition, cond_num)

count(d, ppt) %>% 
  filter(n < 100)
pull(d, ppt) %>% unique() %>% length()
```

TODO: might need to remove kids that don't speak Norwegian at home (see github issue).

```{r predictionsc2l1, fig.cap="C2L1 data. Comparison of 100 simulated (predicted) sets of data to observed data illustated by model. For illustration the x-axis was truncated at 2,000 msecs."}

files <- list.files("../stanout/c2l1", pattern = "sims", full.names = T)
sims <- read_csv(files) %>% 
  pivot_longer(cols = c(y_obs, y_tilde)) %>% 
  mutate(across(name, recode_factor, 
                y_tilde = "Simulated data",
                y_obs = "Observed data",
                .ordered = T)) %>% 
  filter(name ==  "Simulated data" |
         (name == "Observed data" & sim_idx == 1))

```{r}
files <- list.files("../stanout/c2l1", pattern = "^modelcomp", full.names = T)
table <- purrr::map_dfr(files, read_csv) %>% 
  mutate(across(location, replace_na, "overall")) %>% 
  select(location, model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
  mutate(across(where(is.numeric), round, 0),
         across(where(is.numeric), format, big.mark = ","),
         across(everything(), str_trim)) %>%
  transmute(across(location, ~str_c("Text location: ",.)),
            across(model, recode, lmm = "Unimodal log-normal",
                                  lmmgaus = "Unimodal normal",
                                  mog = "Bimodal log-normal",
                                  lmmuneqvar = "Unimodal log-normal (unequal variance)"),
            across(elpd_diff, str_c, " (", se_diff, ")"),
            across(elpd_loo, str_c, " (", se_elpd_loo, ")")) %>% 
  mutate(across(elpd_diff, str_replace, "0 \\(0\\)", "--")) %>% 
  pivot_wider(names_from = location, values_from = contains("elpd")) %>% 
  select(Model = model, 
         ends_with("overall"), 
         ends_with("sent"), 
         ends_with("beforeword"), 
         ends_with("withinword"))

```{r c2l1, results='asis'}
names(table)[-1] <- rep(c("$\\Delta\\widehat{elpd}$", "$\\widehat{elpd}$"),4)

kable(table, caption = "C2L1 data. Model comparisons. The top row shows the models with the highest predictive performance. Standard error is shown in parentheses.",
        align =c("l", rep("r", 8))) %>%
  kable_styling(position = "center", 
                full_width = T, 
                font_size = 11) %>%
  footnote("$\\widehat{elpd}$ = predictive performance indicated as expected log pointwise predictive density; $\\Delta\\widehat{elpd}$ = difference in predictive performance relative to the model with the highest predictive performance in the top row.") %>%
  add_header_above(c(" " = 1, 
                     "All transitions" = 2,
                     "Before sentence" = 2, 
                     "Before word" = 2,
                     "Within word" = 2)) %>%
  column_spec(1, width = "8em")

```{r c2l1post, fig.cap="C2l1. Posterior parameter distribution"}
file <- list.files(path = "../stanout/c2l1", pattern = "mog.csv$",full.names = T)
ps <- read_csv(file) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(delta, ~.+beta),
         across(c(delta, beta), exp),
         across(delta, ~.-beta),
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(beta:prob) %>% 
  group_by(location, name) %>% 
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"))

beta <- filter(ps, name == "beta") %>% 
  mutate(name = beta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = 1:4) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = scales::comma) +
  labs(y = "Posterior estimate with 95% PIs",
       x = "",
       colour = "",
       shape = "") +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

delta <- filter(ps, name == "delta") %>% 
  mutate(name = delta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = 1:4) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "",
       x = "Transition location",
       colour = "",
       shape = "") +
  theme(axis.title.y = element_blank()) +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

theta <- filter(ps, name == "prob") %>% 
  mutate(name = theta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = 1:4) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = dezero_plot, limits = c(0, 1)) +
  labs(y = "",
       x = "",
       colour = "",
       shape = "") +
  theme(axis.title.y = element_blank()) +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

# CATO

Data are published in @torrance2016adolescent. Norwegian upper
secondary students--*N*=26, mean age = 16.9 years--with weak decoding skills and 26 age-matched controls composed expository texts by keyboard under two conditions: normally and with letters masked to prevent them reading what they were writing.

```{r predictionscato, fig.cap="CATO data. Comparison of 100 simulated (predicted) sets of data to observed data illustated by model. For illustration the x-axis was truncated at 2,000 msecs."}

files <- list.files("../stanout/cato", pattern = "sims", full.names = T)
sims <- read_csv(files) %>% 
  pivot_longer(cols = c(y_obs, y_tilde)) %>% 
  mutate(across(name, recode_factor, 
                y_tilde = "Simulated data",
                y_obs = "Observed data",
                .ordered = T)) %>% 
  filter(name ==  "Simulated data" |
         (name == "Observed data" & sim_idx == 1))

```{r}
files <- list.files("../stanout/cato", pattern = "^modelcomp", full.names = T)
table <- purrr::map_dfr(files, read_csv) %>% 
  mutate(across(location, replace_na, "overall")) %>% 
  select(location, model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
  mutate(across(where(is.numeric), round, 0),
         across(where(is.numeric), format, big.mark = ","),
         across(everything(), str_trim)) %>%
  transmute(across(location, ~str_c("Text location: ",.)),
            across(model, recode, lmm = "Unimodal log-normal",
                                  lmmgaus = "Unimodal normal",
                                  mog = "Bimodal log-normal",
                                  lmmuneqvar = "Unimodal log-normal (unequal variance)"),
            across(elpd_diff, str_c, " (", se_diff, ")"),
            across(elpd_loo, str_c, " (", se_elpd_loo, ")")) %>% 
  mutate(across(elpd_diff, str_replace, "0 \\(0\\)", "--")) %>% 
  pivot_wider(names_from = location, values_from = contains("elpd")) %>% 
  select(Model = model, 
         ends_with("overall"), 
         ends_with("sent"), 
         ends_with("beforeword"), 
         ends_with("withinword"))

```{r cato, results='asis'}
names(table)[-1] <- rep(c("$\\Delta\\widehat{elpd}$", "$\\widehat{elpd}$"),4)

kable(table, caption = "CATO data. Model comparisons. The top row shows the models with the highest predictive performance. Standard error is shown in parentheses.",
        align =c("l", rep("r", 8))) %>%
  kable_styling(position = "center", 
                full_width = T, 
                font_size = 11) %>%
  footnote("$\\widehat{elpd}$ = predictive performance indicated as expected log pointwise predictive density; $\\Delta\\widehat{elpd}$ = difference in predictive performance relative to the model with the highest predictive performance in the top row.") %>%
  add_header_above(c(" " = 1, 
                     "All transitions" = 2,
                     "Before sentence" = 2, 
                     "Before word" = 2,
                     "Within word" = 2)) %>%
  column_spec(1, width = "8em")

```{r catopost, fig.cap="CATO. Posterior parameter distribution"}
file <- list.files(path = "../stanout/cato", pattern = "mog.csv$",full.names = T)
ps <- read_csv(file) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(delta, ~.+beta),
         across(c(delta, beta), exp),
         across(delta, ~.-beta),
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(beta:prob) %>% 
  group_by(task, group, location, name) %>% 
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}")) %>% 
  mutate(task = str_c("Task: ", task, "; Group: ", group))

beta <- filter(ps, name == "beta") %>% 
  mutate(name = beta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = 1:4) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = scales::comma) +
  labs(y = "Posterior estimate with 95% PIs",
       x = "",
       colour = "",
       shape = "") +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

delta <- filter(ps, name == "delta") %>% 
  mutate(name = delta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = 1:4) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "",
       x = "Transition location",
       colour = "",
       shape = "") +
  theme(axis.title.y = element_blank()) +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

theta <- filter(ps, name == "prob") %>% 
  mutate(name = theta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = 1:4) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = dezero_plot, limits = c(0, 1)) +
  labs(y = "",
       x = "",
       colour = "",
       shape = "") +
  theme(axis.title.y = element_blank()) +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

@@

@@

# PLanTra

@@

The PLanTra (Plain Language for Financial Content: Assessing the Impact of Training on Students' Revisions and Readers' Comprehension) data set [@rossetti2022s] involved the collection of keystroke data from 47 university students, who were randomly divided into an experimental and a control group. In a pre-test session, all students were assigned an extract of a corporate report dealing with sustainability and were instructed to revise it to make it easier to read for a lay audience. Subsequently, the experimental group received training on how to apply plain language principles to sustainability content, while the control group received training exclusively on the topic of sustainability. During a post-test session, both groups were instructed to revise a second extract of a corporate sustainability report with the same goal--i.e. making it easier to read for a lay audience--by applying what they had learned from their respective training. The texts were in English while the participants were native speakers of other languages (mainly Dutch), so writing took place in second language. It should be pointed out that, while some students decided to revise the assigned texts, the majority of them opted for rewriting the texts from scratch.

@@

```{r predictionsplantra, fig.cap="PLanTra data. Comparison of 100 simulated (predicted) sets of data to observed data illustated by model. For illustration the x-axis was truncated at 2,000 msecs."}

@@

kable(table, caption = "PLanTra data. Model comparisons. The top row shows the models with the highest predictive performance. Standard error is shown in parentheses.",
        align =c("l", rep("r", 8))) %>%
  kable_styling(position = "center", 
                full_width = T, 
                font_size = 11) %>%
  footnote("$\\widehat{elpd}$ = predictive performance indicated as expected log pointwise predictive density; $\\Delta\\widehat{elpd}$ = difference in predictive performance relative to the model with the highest predictive performance in the top row.") %>%
  add_header_above(c(" " = 1, 
                     "All transitions" = 2,
                     "Before sentence" = 2, 
                     "Before word" = 2,
                     "Within word" = 2)) %>%
  column_spec(1, width = "8em")

@@

```{r plantrapost, fig.cap="PLanTra. Posterior parameter distribution"}
file <- list.files(path = "../stanout/plantra", pattern = "mog.csv$",full.names = T)
ps <- read_csv(file) %>% 
  mutate(across(task, factor, levels = c("pre-test", "post-test"), ordered = T)) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(delta, ~.+beta),
         across(c(delta, beta), exp),
         across(delta, ~.-beta),
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(beta:prob) %>% 
  group_by(task, location, name) %>% 
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"))

beta <- filter(ps, name == "beta") %>% 
  mutate(name = beta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = c(21, 23)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "Posterior estimate with 95% PIs",
       x = "",
       colour = "Task",
       shape = "Task") +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

delta <- filter(ps, name == "delta") %>% 
  mutate(name = delta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = c(21, 23)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "",
       x = "Transition location",
       colour = "Task",
       shape = "Task") +
  theme(axis.title.y = element_blank()) +
    guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

theta <- filter(ps, name == "prob") %>% 
  mutate(name = theta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = task,
             shape = task)) +
  geom_point(size = 3, position = position_dodge(.25)) +
  geom_errorbar(width = 0, position = position_dodge(.25)) +
  facet_grid(~name) +
  scale_shape_manual(values = c(21, 23)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = dezero_plot, limits = c(0, 1)) +
  labs(y = "",
       x = "",
       colour = "Task",
       shape = "Task") +
  theme(axis.title.y = element_blank()) +
    guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

@@

LIFT (Improving Pre-university Students' Performance in Academic Synthesis Tasks with Level-up Instructions and Feedback Tool) [@nina_vandermeulen_2020_3893538].

@@

```{r}
files <- str_c("../stanout/", 
               c("lift", "spl2", "plantra", "cato", "c2l1"), 
               "/mog.csv")
ps <- purrr::map_dfr(files, ~read_csv(.x) %>% 
  mutate(data = .x)) %>% 
  mutate(across(data, str_remove_all, 
                "\\.|\\/|stanout|\\mog.csv"),
         across(data, recode_factor, 
                "cato" = "CATO (non-dyslexic\nunmasked)",
                "spl2" = "SPL2 (L1)", 
                "plantra" = "PLanTra",
                "lift" = "LIFT",
                "c2l1" = "C2L1",
                .ordered = TRUE)) %>% 
  filter(!(str_detect(data, "SPL2") & lang == "ES"),
         !(str_detect(data, "CATO") & group == "dyslexic"),
         !(str_detect(data, "CATO") & task == "masked")) %>% 
#  filter(str_detect(data, "CATO"))
  pivot_wider(names_from = param, 
              values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(delta, ~.+beta),
         across(c(delta, beta), exp),
         across(delta, ~.-beta),
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(beta:prob) %>% 
  group_by(data, location, name) %>% 
  summarise(across(value, 
                   list(mean = mean, 
                        lower = lower, 
                        upper = upper),
                   .names = "{.fn}")) %>% 
  ungroup()
```

```{r crossstudypost, fig.cap="Across studies. Posterior parameter distribution"}
posd <- position_dodge(.65)
dotsize <- 2.5
grouplabel <- "Data set"
beta <- filter(ps, name == "beta") %>% 
  mutate(name = beta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = data,
             shape = data,
             group = interaction(data))) +
  geom_line(size = .5, alpha = .35, position = posd) +
  geom_point(size = dotsize, position = posd) +
  geom_errorbar(width = 0, position = posd) +
  facet_grid(~name) +
  scale_shape_manual(values = c(1, 4, 7, 8, 9)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "Posterior estimate with 95% PIs",
       x = "",
       colour = grouplabel,
       shape = grouplabel) +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

delta <- filter(ps, name == "delta") %>% 
  mutate(name = delta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = data,
             shape = data,
             group = interaction(data))) +
  geom_line(size = .5, alpha = .35, position = posd) +
  geom_point(size = dotsize, position = posd) +
  geom_errorbar(width = 0, position = posd) +
  facet_grid(~name) +
  scale_shape_manual(values = c(1, 4, 7, 8, 9)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "",
       x = "Transition location",
       colour = grouplabel,
       shape = grouplabel) +
  theme(axis.title.y = element_blank()) +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

theta <- filter(ps, name == "prob") %>% 
  mutate(name = theta_label) %>% 
  ggplot(aes(y = mean, 
             ymin = lower, 
             ymax = upper,
             x = location,
             colour = data,
             shape = data,
             group = interaction(data))) +
  geom_line(size = .5, alpha = .35, position = posd) +
  geom_point(size = dotsize, position = posd) +
  geom_errorbar(width = 0, position = posd) +
  facet_grid(~name) +
  scale_shape_manual(values = c(1, 4, 7, 8, 9)) +
  scale_colour_viridis_d(end = .7) +
  scale_y_continuous(labels = dezero_plot, limits = c(0, 1)) +
  labs(y = "",
       x = "",
       colour = grouplabel,
       shape = grouplabel) +
  theme(axis.title.y = element_blank()) +
  guides(colour=guide_legend(nrow=2,byrow=TRUE),
         shape = guide_legend(nrow=2,byrow=TRUE))

@@

```{r eval = F}
# use posterior to calculate interactions, cell means and dataset differences
files <- str_c("../stanout/", c("lift", "spl2", "plantra", "cato", "c2l1"), "/mog.csv")

@@

cato <- read_csv(files[4], id = "data") %>% 
  pivot_wider(names_from = c(task, group), values_from = value) %>% 
  unnest() %>% 
  rowwise() %>% 
  mutate(value = mean(c_across(contains("_")))) %>% 
  ungroup() %>% 
  select(param, location, value, data)

c2l1 <- read_csv(files[5], id = "data") %>% 
  select(param, location, value, data)

ps <- bind_rows(plantra, spl2, lift, cato, c2l1) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta, delta, prob)) %>% 
  mutate(across(data, 
                str_remove_all, 
                "\\.|\\/|stanout|\\mog.csv"),
         theta = logit_scaled(prob)) %>% 
  select(-prob) %>%
  pivot_longer(beta:theta) %>%
  pivot_wider(names_from = c(data, location), 
              values_from = value, 
              names_sep = "_") %>% 
  unnest(contains("_"))

# Get main effects, interactions, nested effects
ps_effects <- ps %>%
  rowwise() %>%
  mutate(# Main effects
         DS_1 = mean(c_across(starts_with("lift_"))) - 
                mean(c_across(starts_with("spl2_"))),
         DS_2 = mean(c_across(starts_with("lift_"))) - 
                mean(c_across(starts_with("plantra_"))),
         DS_3 = mean(c_across(starts_with("spl2_"))) - 
                mean(c_across(starts_with("plantra_"))),
         DS_4 = mean(c_across(starts_with("lift_"))) - 
                mean(c_across(starts_with("cato_"))),
         DS_5 = mean(c_across(starts_with("plantra_"))) - 
                mean(c_across(starts_with("cato_"))),
         DS_6 = mean(c_across(starts_with("spl2_"))) - 
                mean(c_across(starts_with("cato_"))),
         DS_7 = mean(c_across(starts_with("c2l1_"))) - 
                mean(c_across(starts_with("plantra_"))),
         DS_8 = mean(c_across(starts_with("c2l1_"))) - 
                mean(c_across(starts_with("cato_"))),
         DS_9 = mean(c_across(starts_with("c2l1_"))) - 
                mean(c_across(starts_with("spl2_"))),
         DS_10 = mean(c_across(starts_with("c2l1_"))) - 
                mean(c_across(starts_with("lift_"))),

         TL_1 =  mean(c_across(contains(" sentence"))) - 
                mean(c_across(contains("_before word"))),
         TL_2 =  mean(c_across(contains("_before"))) - 
                mean(c_across(contains("_within word"))),
         # Two-way interactions
         `DS_1:TL_1` = (`lift_before sentence` - `lift_before word`) -
                       (`spl2_before sentence` - `spl2_before word`),

@@

         `DS_4:TL_1` = (`lift_before sentence` - `lift_before word`) -
                       (`cato_before sentence` - `cato_before word`),

         `DS_5:TL_1` = (`plantra_before sentence` - `plantra_before word`) - 
                       (`cato_before sentence` - `cato_before word`),

         `DS_6:TL_1` = (`spl2_before sentence` - `spl2_before word`) -
                       (`cato_before sentence` - `cato_before word`),

         `DS_7:TL_1` = (`c2l1_before sentence` - `c2l1_before word`) -
                       (`plantra_before sentence` - `plantra_before word`),

         `DS_8:TL_1` = (`c2l1_before sentence` - `c2l1_before word`) -
                       (`cato_before sentence` - `cato_before word`),

         `DS_9:TL_1` = (`c2l1_before sentence` - `c2l1_before word`) -
                       (`spl2_before sentence` - `spl2_before word`),

         `DS_10:TL_1` = (`c2l1_before sentence` - `c2l1_before word`) -
                        (`lift_before sentence` - `lift_before word`),

@@

```{r cellmeans, results = 'asis'}
tmp <- read_csv("tables/cellmeans_transdur.csv")
